An Implementation of the Active Contours without Edges Model and the Logic Framework for Active Contours on Multi-channel Images

### 2010-12-13 trunk/cs870/project/Report/Paper.tex
Final commit isA isA isA

During implementation, we tried to stick to the authors' formulas and guidelines as much as possible. In this section we explain what methods we use to
numerically solve the PDEs. For the chan-vese model, we use the PDE given in Equation 9 in the original paper~\cite{chan2001active} which is shown in
Equation~\ref{eqn:cvpde}.  We, first, tried to implement the dirac delta function, $\delta_{\varepsilon}\phi$, as defined in the paper. However, it resulted in
worse segmentations. Accordingly, we chose to use $|\bigtriangledown\phi|$ instead of the dirac delta function as this
was indicated as a valid alternative by the authors. To calculate $c_{1}$ and $c_{2}$, we simply calculated the mean of the values inside $\phi$ (specifically
where $\phi > 0$) and the mean of the values outside $\phi$ (specifically where $\phi < 0$) respectively. To actually solve the PDE, we chose to use an explicit
time stepping scheme for the finite difference discretization. That is, in each time step $\phi^{n+1} = \phi^n + \triangle t*phi_t$. This was simpler to
implement, and although $\triangle t$ must be chosen carefully to satisfy the stability condition ($\triangle t <= (1/imageSize)^2$), we did not suffer from
performance problems due to this restriction.

@@

\begin{figure}[h!]
\centering
\includegraphics[width=0.3\textwidth]{family.png}
\caption{Combining missing information from two different channels. Size = 114 x 114. $\phi_{0}(x,y) = \sqrt{(x - 57)^2 + (y - 57)^2} -
28.5$, no reinitialization. Union: cpu = 4.01 s and iterations = 7. Intersection: cpu = 4.12 s and iterations = 7.}
\label{fig:family}
\end{figure}

\begin{figure*}[t!]
\centering
\includegraphics[width=12cm]{donutlogic.png}
\caption{Performing union and intersection on images with holes. Size = 300 x 300. $\phi_{0}(x,y) = - \sqrt{(x - 150)^2 + (y - 150)^2)} +
75$, no reinitialization. For union: cpu = 8.63 sec and iterations = 10. For intersection: cpu = 7.68 sec and iterations = 10.}
\label{fig:donutlogic}
\end{figure*}

\begin{figure}[t!h!]
\centering
\includegraphics[width=0.3\textwidth]{diffint.png}
\caption{Segmentation for union and intersection of channels having reverse contrast.. Size = 300 x 300, $\phi_{0}(x,y) = - \sqrt{(x - 150)^2 + (y - 150)^2)} +
75$,  no reinitialization. For union: cpu = 1.32 sec and iterations = 2. For intersection: cpu = 1.83 sec and iterations = 2}
\label{fig:diffint}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.4\textwidth]{sc_blurry.png}
\caption{Successful union with blurred images. Top: the evolving curve for $A_1 \cup A_2$
(in red) over time where the first
image shows the initial
contour. Bottom: evolving segmentation over time until the union is detected. Size = 200 x 200, $\phi_{0}(x,y) = - \sqrt{(x - 100)^2 + (y - 100)^2)} +
50$, no reinitialization, cpu = 6 s, iterations = 11.}
\label{fig:sc_blurry}
\end{figure}

@@

\begin{figure*}[t!]
\centering
\includegraphics[width=12cm]{flowers.png}
\caption{Ability to detect the full contour on a colored image with low variation between foreground and background by taking the union of the RGB channels.
Full contour detected as opposed to Figure~\ref{fig:cv_eg7}. Size = 300 x 300, $\phi_{0}(x,y) = - \sqrt{(x - 150)^2 + (y - 150)^2)} + 75$, no reinitialization,
size = cpu = 1.73 sec, iterations = 7.}
\label{fig:flowers}
\end{figure*}

@@

\subsection{Defining the initial contour $phi_0$}
Both the Chan-Vese model and the Sandberg-Chan model define the initial contour ($\phi_0$) as a signed distance function where $\phi_0$ is positive inside the
contour $C$, zero on the boundary of $C$ ($\partial C$), and negative outside the contour $C$. Figure~\ref{fig:phinote} illustrates those assumptions.

>>>>

During implementation, we tried to stick to the authors' formulas and guidelines as much as possible. In this section we explain what methods we use to
numerically solve the PDEs. For the chan-vese model, we use the PDE given in Equation 9 in the original paper~\cite{chan2001active} which is shown in
Equation~\ref{eqn:cvpde}.  We, first, tried to implement the dirac delta function, $\delta_{\varepsilon}\phi$, as defined in the paper. However, it resulted in
worse segmentations. Accordingly, we chose to use $|\bigtriangledown\phi|$ instead of the dirac delta function as this
was indicated as a valid alternative by the authors. To calculate $c_{1}$ and $c_{2}$, we simply calculated the mean of the values inside $\phi$ (specifically
where $\phi > 0$) and the mean of the values outside $\phi$ (specifically where $\phi < 0$) respectively. To actually solve the PDE, we chose to use an explicit
time stepping scheme for the finite difference discretization. That is, in each time step $\phi^{n+1} = \phi^n + \triangle t*\phi_t$. This was simpler to
implement, and although $\triangle t$ must be chosen carefully to satisfy the stability condition ($\triangle t <= (1/imageSize)^2$), we did not suffer from
performance problems due to this restriction.

@@

\begin{figure*}[t!]
\centering
\includegraphics[width=0.3\textwidth]{family.png}
\caption{Combining missing information from two different channels. Size = 114 x 114. $\phi_{0}(x,y) = \sqrt{(x - 57)^2 + (y - 57)^2} -
28.5$, no reinitialization. Union: cpu = 4.01 s and iterations = 7. Intersection: cpu = 4.12 s and iterations = 7.}
\label{fig:family}
\end{figure*}

\begin{figure*}[t!]
\centering
\includegraphics[width=0.5\textwidth]{donutlogic.png}
\caption{Performing union and intersection on images with holes. Size = 300 x 300. $\phi_{0}(x,y) = - \sqrt{(x - 150)^2 + (y - 150)^2)} +
75$, no reinitialization. For union: cpu = 8.63 sec and iterations = 10. For intersection: cpu = 7.68 sec and iterations = 10.}
\label{fig:donutlogic}
\end{figure*}

\begin{figure}[h!]
\centering
\includegraphics[width=0.3\textwidth]{diffint.png}
\caption{Segmentation for union and intersection of channels having reverse contrast.. Size = 300 x 300, $\phi_{0}(x,y) = - \sqrt{(x - 150)^2 + (y - 150)^2)} +
75$,  no reinitialization. For union: cpu = 1.32 sec and iterations = 2. For intersection: cpu = 1.83 sec and iterations = 2}
\label{fig:diffint}
\end{figure}

@@

\begin{figure*}[t]
\centering
\includegraphics[width=0.3\textwidth]{sc_blurry.png}
\caption{Successful union with blurred images. Top: the evolving curve for $A_1 \cup A_2$
(in red) over time where the first
image shows the initial
contour. Bottom: evolving segmentation over time until the union is detected. Size = 200 x 200, $\phi_{0}(x,y) = - \sqrt{(x - 100)^2 + (y - 100)^2)} +
50$, no reinitialization, cpu = 6 s, iterations = 11.}
\label{fig:sc_blurry}
\end{figure*}

\begin{figure*}[t!h!]
\centering
\includegraphics[width=0.5\textwidth]{flowers.png}
\caption{Ability to detect the full contour on a colored image with low variation between foreground and background by taking the union of the RGB channels.
Full contour detected as opposed to Figure~\ref{fig:cv_eg7}. Size = 300 x 300, $\phi_{0}(x,y) = - \sqrt{(x - 150)^2 + (y - 150)^2)} + 75$, no reinitialization,
size = cpu = 1.73 sec, iterations = 7.}
\label{fig:flowers}
\end{figure*}

@@

@@

\subsection{Defining the initial contour $\phi_0$}
Both the Chan-Vese model and the Sandberg-Chan model define the initial contour ($\phi_0$) as a signed distance function where $\phi_0$ is positive inside the
contour $C$, zero on the boundary of $C$ ($\partial C$), and negative outside the contour $C$. Figure~\ref{fig:phinote} illustrates those assumptions.
